\documentclass[12pt, titlepage]{article}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=magenta]{hyperref}

\title{Feedback Controls Lab Weekly Report \\ \normalsize{Week 16}}
\author{Aydan Vissing, Brady Schick, Gabriel Southwell, Simon Ross}
\date{\today}

\begin{document}
\maketitle

\section*{Aydan Vissing (5 hours spent)}

We spent time on our presentation and listening to others, as well as our weekly meeting. After this, I spent time with the gyro test mount model from thingiverse to see if it would fit on our 3d printers. It is going to take some fancy editing to make it fit but I can make it fit. I am going to work on this over break. My next focus is going to be on the final report. 

\section*{Brady Schick (4 hours spent)}

This was a very busy week outside of senior design, and not much got done on my part. Other than our presentation on Tuesday and our weekly meeting on Friday, I did a small amount of work on linearizing the mathematical model. Depending on how busy I am, I will plan to get that done and also update the coordinate system over the break.

\section*{Gabriel Southwell (6 hours spent)}

I devoted a significant amount of time to preparing my part of the presentation. Not sure if I can count the time spent watching other presentations

This week I also started working on cleaning up all my source code an documenting things. Everything that I have written this semester is more or less in just one big file that I am breaking up into smaller component files. This will make the codebase much more readable and easier to debug

\section*{Simon Ross (2.25 hours spent)}

I did presentation work and our meeting this week. I'm hoping to get a little work done over break on the project, which should be possible now since the boards came in. This upcoming week I'll be working on the report.


\end{document}